### 2021-02-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

\section{Contribution}
To address Problem 1, we make the following contributions on detecting side-channel leakages:

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We first present relevant backgrounds and related works in Chapter~\ref{chapter1}. We then propose our works in
Chapter~\ref{chapter2}. Chapter~\ref{chapter3} and Chapter~\ref{chapter4} introduce
our recent progress about the proposed work.

>>>>

\section{Contribution}
We address the above problems from two aspects. First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely. Second, we propose methods that can quantify each side-channel leakages precisely. In additional, we study two kinds of threat models, a single trace attack, and chosen message attacks

In summary, we make the following contributions:

To address Problem 1, we make the following contributions on detecting side-channel leakages:

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present relevant backgrounds and related works in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} present a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extend the approach and quantifies the side-channel leakage in chosen message attacks. Chapter~\ref{chapter6} conclude the thesis.
